\documentclass[../Main.tex]{subfiles}
\pagenumbering{roman}
\begin{document}
\begin{center}
    \Large{\textbf{PREFACE}}\\
\end{center}
\vspace{1cm}
In the current era of rapid technological advancement, the development of software and applications has significantly enhanced productivity and efficiency across various tasks.
Information technology has been widely integrated into different socio-economic sectors, revolutionizing traditional processes.
Among these, the education sector, particularly student accommodation, is ripe for innovation.
The task of finding suitable hostels and compatible roommates is often a challenging and time-consuming endeavor for students.
Recognizing this, the project aims to design and build a website that simplifies locating hostels and selecting roommates.

This website will serve as a comprehensive platform where students can search for available accommodation options and connect with potential roommates.
By leveraging modern web technologies, the site will offer a user-friendly interface, real-time updates, and personalized recommendations, streamlining the search and selection process.

I would like to express my deepest gratitude to Ph.D. Nguyen Quang Minh, whose guidance and valuable insights have been instrumental throughout the development of this project.
I am also thankful for the experiences gained during my academic journey, which have been pivotal in the execution of this thesis.
Due to the limited timeframe and the scope of knowledge required for such an undertaking, there may be imperfections in the project’s execution.
I am open to and eagerly await constructive feedback that will refine my knowledge and enhance the quality of my future work.

In closing, I wish Ph.D. Nguyen Quang Minh continued health and success in their noble pursuit of education.
Once again, I extend my heartfelt thanks.
\end{document}
