\documentclass[../Main.tex]{subfiles}
\begin{document}
\section{Conclusion}
After researching and analyzing, I have developed a website system to support finding rental houses for my graduation project.
Using the programming skills and knowledge I have acquired, such as JavaScript, HTML, CSS, Java Spring Boot, and MySQL database, I have created a complete system.

This system can bring many benefits to users, allowing people to easily search for rental information and post listings effortlessly.
In particular, the website features a dedicated management page for landlords, helping them manage their listings easily.

Applying modern programming skills and technologies like Java Spring Boot and MySQL has helped me create a reliable and efficient system.
I utilized the data processing and logic capabilities of the Spring framework to build APIs that support searching for rental information and revenue statistics.
Additionally, by using MySQL, I stored and queried data effectively to ensure the system runs smoothly and reliably.

Moreover, working on this project has helped me apply and hone my programming, project management, and testing skills.
I learned how to build a complex project from start to finish, from requirement analysis, system design, implementation, to testing.
This experience has enhanced my ability to work independently, manage time, and solve issues that arise during development.

However, like any development project, my system still has some shortcomings and room for improvement.
In the future, I will continue to upgrade and develop the system to better meet user requirements.
I will keep learning and applying new and advanced techniques to improve the system's performance and features.
I aim to optimize the code and improve the user interface to provide the best user experience.

I am confident that the knowledge and skills I have gained from this project will continue to contribute to my growth in the software development field.

\section{Future work}
Due to my limited capabilities and the short time frame for implementation, the project has not fully met all the functionalities that a rental search website requires.
Therefore, to make the project more comprehensive, practical, and highly applicable, it needs to be supplemented with additional features.

I propose developing the following additional features:

\begin{itemize}
    \item Integration with Facebook and Google accounts
    \item Adding a chat function between landlords and tenants
    \item Adding a feature to search for rooms in nearby locations using Google Maps
\end{itemize}

\end{document}
